Speakers of diverse languages structure their utterances for efficient communication

### 2019-11-05 Paper/info-curves.Rmd
edits to bnc & switchboard in paper

We train an ngram language model on a given corpusm with order set to $1$ for the frequency-model, $2$ for a bigram model and $3$ for a trigram model. An ngram language model produces a probability for each continuation of each $n-1$ words it receives as input. Models with order greater than $3$ have issues with overfitting to the corpus. In our contextual models, we face another issue of overfitting: we only train our model on those utterances which occur in the corpus and test our model on the same utterances. This ignores possible other utterances which the speakers could have produced, e.g. the words "I", "saw" and "bears" are in the corpus vocabulary, which the speaker may not have produced in the corpus but could have produced. To combat this issue, we use modified Kneser-Ney smoothing as implemented in the KenLM toolkit [@heafield2013scalable]. Briefly, this smoothing technique discounts all ngram counts, which reduces the impact of rare ngrams on probability calculations, and interpolates lower-order ngrams into the calcuations. These lower-order ngrams are weighted according to the number of distinct contexts they occur as a continuation (e.g. "Francisco" may be a common word in a corpus, but likely only occurs after "San" as in "San Francisco", so it receives a lower weighting). For a full explanation of modified Kneser-Ney smoothing, see @chen1999empirical.

@@

We first replicate the @yu2016 result using the surprisal metric in place of the entropy metric. We use the frequency-based or “contextless” surprisal metric, which determines the average distribution of information based on word frequencies in a corpus. A priori we expect that the frequency-based metric will produce a flat distribution of information across word positions in the BNC.

See in Figure \@ref(fig:bnc_unigrams) a qualitative comparison of the information trajectory they found and the information trajectory we found. It is easily observable that the two information trajectories are identical, and we have found the same distribution of information in the BNC as @yu2016 did. The first words in written English sentences tend to contain little information, while the final words tend to contain a great deal of information.

@@

However, this only characterizes written English sentences. If this information distribution is characteristic more generally of English, then we will find the same distribution for spoken English. We use the Switchboard corpus of spoken English telephone conversations between adults to compute the distribution of information across spoken utterances in English. The sentences in the BNC, compared to the conversations in Switchboard, feature much longer sentences with larger vocabularies and more complex sentence structures. We split the conversations in Switchboard not by sentences, as in the BNC, but by turns.

For Switchboard we find the same information trajectory as we did for the BNC, and we find the same distribution of information regardless of utterance length. The longer the utterance, the more pronounced the information distribution shape becomes. A qualitative comparison of the two trajectories is in Figure \@ref(fig:switchboard_unigrams).

>>>>

We train an ngram language model on a given corpus with order set to $1$ for the frequency-model, $2$ for a bigram model and $3$ for a trigram model. An ngram language model produces a probability for each continuation of each $n-1$ words it receives as input. Models with order greater than $3$ have issues with overfitting to the corpus, while bigram models generally underperform trigram models. In our contextual models, we face another issue of overfitting: we only train our model on those utterances which occur in the corpus and test our model on the same utterances. This ignores possible other utterances which the speakers could have produced, e.g. the words "I", "saw" and "bears" are in the corpus vocabulary, which the speaker may not have produced in the corpus but could have produced. To combat this issue, we use modified Kneser-Ney smoothing as implemented in the KenLM toolkit [@heafield2013scalable]. Briefly, this smoothing technique discounts all ngram counts, which reduces the impact of rare ngrams on probability calculations, and interpolates lower-order ngrams into the calcuations. These lower-order ngrams are weighted according to the number of distinct contexts they occur as a continuation (e.g. "Francisco" may be a common word in a corpus, but likely only occurs after "San" as in "San Francisco", so it receives a lower weighting). For a full explanation of modified Kneser-Ney smoothing, see @chen1999empirical.

@@

We replicate the @yu2016 result using the surprisal metric in place of the entropy metric. We use the frequency-based or “contextless” surprisal metric, which determines the average distribution of information based on word frequencies in a corpus. A priori we expect that the frequency-based metric will produce a flat distribution of information across word positions in the BNC.

We find the same frequency-based information trajectory as Yu et al. with little information in the first words of utterances and the most information in the final word, see \@ref(fig:bnc_unigrams).

@@

However, we have only found an information distribution for written English sentences in a single British English corpus. We predict that this frequency-based distribution will also hold for sentences spoken English. To show this, we use the Switchboard corpus of spoken American English telephone conversations. As a collection of written texts, our subset of the BNC features much longer sentences with a larger vocabulary per text and overall more complex sentence structures than Switchboard. We split the conversations in Switchboard not by sentences, as in the BNC, but by conversational turns.

For Switchboard we find the same frequency-based information distribution as the BNC, as seen in \@ref(fig:switchboard_unigrams). Notice in Figure \@ref(fig:switchboard_unigrams) that the longer the utterance length for Switchboard, the more clearly the information distribution for that utterance length characterizes
